mruby Bytecode Loader Using Bluetooth in Multi-VM Environment

### 2016-01-25 thesis/diff/0125_thesis.tex
add diff

\begin{document}
\maketitle

\begin{abstract}
In recent years, the productivity of embedded systems has become a problem due to their complexity and large-scale.
For the purpose of improving the productivity for embedded software development, the mruby on TECS framework has been proposed that is applied mruby (Lightweight Ruby) and supports component-based development.
In the current mruby on TECS, the mruby programs have to be compiled and linked every time the programs are modified because the mruby bytecodes are incorporated in the platform.
Moreover, while the framework supports multi-VM, developers needs to be familiar with the functions of real-time operating systems to effectively execute multiple mruby programs in concurrent or/and parallel.
In this paper, to improve the development efficiency, the mruby bytecode loader using Bluetooth is implemented as an extension of mruby on TECS.
In addition, multiple mruby programs run cooperatively in the proposed framework.
Experimental results demonstrates the advantages of the proposed framework.
\end{abstract}
\section{Introduction}
In these days, embedded systems have been required the high-quality and the high-performance.
Due to this trend, the complexity of embedded systems also increases and the scale is larger.
For example, IoT (Internet of Things) applications.
The low production cost and the short developing period of time are also needed.

@@

This paper proposes two additional features of mruby on TECS, mruby bytecode loader using Bluetooth and user-friendly multitask.
mruby on TECS has some problems at present.
One of these is that working efficiency is low because mruby on TECS only supports a SD card in the platform for LEGO MINDSTORMS EV3 to load mruby programs.
In the current development process, it is annoying that the SD card should be insert and pulled out repeatedly.
If a new feature, mruby bytecode loader Bluetooth, is used, the procedure is carried out only once at the beginning and a program code is transferred from a host to a target device by Bluetooth.
It can improve the efficiency.
Moreover, in the current system if developers attempt to run multiple tasks with the same priority, a task with first execution only runs and all other tasks would not run unless a OS's function must be called by developers.
In addition developers must prepare as many VMs as the number of threads because one RiteVM supports only one thread.
Thus that is a big burden on developers.
Another new feature enables developers to run a multitask programs more easily.
Specifically, a cycle handler of switching tasks is implemented.
This paper evaluates the proposed framework in term of data transfer rate, overhead of cyclic handler and execution time.
\\

{\bf Contributions}
\begin{enumerate}
\item To improve the  work efficiency in software development on mruby on TECS: \mbox{}\\
\ mruby bytecode loader using Bluetooth helps developers develop software.
Developers do not need to insert and pull out repeatedly, and that improves the software development efficiency.
\item To effectively execute multiple mruby programs in concurrent or/and parallel: \mbox{}\\
\ There is a probrem in multitasking of the current mruby on TECS.
It is that developers need to be well acquainted the RTOS if multiple mruby programs execute in multitasking. 
In the proposed framework, it is easy for developers to use multitasking because multiple tasks are switched cyclically.
Developers can easily program multitasking.
Multitasked programing makes the range of software expand.
\end{enumerate}

The paper is organized as follows:
Section \ref{sec:Background} introduces the basic technologies i.e. mruby, TECS and mruby on TECS.
Section \ref{sec:mruby bytecode loader using Bluetooth} and Section \ref{sec:Multitask} describe the design and implementation of the proposed framework in detail.
Section \ref{sec:Evaluation} evaluates the proposed framework, Section \ref{sec:Related work} discuses related work, and then Section \ref{sec:Conclusion} concludes.

@@

\section{Evaluation}
\label{sec:Evaluation}
To analyze the advantages and disadvantages of the proposed framework, the evaluations are performed as follows.
\begin{itemize}
        \item the comparison of the size and transfer time between an mruby application including mruby libraries and not.
        \item the comparison of the overheads for each cyclic period of calling rot\_rdq.
        \item the comparison of the application execution time with singletasking, co-routine and multitasking.
\end{itemize}

@@

@@

\begin{table*}[t]
    \centering
    \caption{Comparion of the proposed and previous work}
    \begin{tabular}{c||c|ccc}
        & \shortstack{mruby bytecode loader\\using Bluetooth} & \shortstack{Preemptive-multitask\\(multi-VM)} & \shortstack{Nonpreemptive-multitask\\(co-routine)} & GIL \\ \hline
        mruby on TECS& & \checkmark & \checkmark & \\
        mruby & & & \checkmark &\\
        Owl system & & \checkmark & & \checkmark \\
        Lua & & \checkmark & \checkmark \\
        Proposed framework& \checkmark & \checkmark & \checkmark \\
    \end{tabular}
    \label{tab:comparion}
\end{table*}
The open-source run-time systems for scripting languages have been developed such as follow: mruby on TECS \cite{7153813}, mruby \cite{5959588}, the Owl system \cite{180964}, and Lua \cite{Ierusalimschy:2007:EL:1238844.1238846}

@@

\section{Conclusion}
\label{sec:Conclusion}

%&=& &=& &=& 
% Reference
%&=& &=& &=& 
\bibliography{ref.bib}

>>>>

\begin{document}
\maketitle
\begin{abstract}
In recent years, the productivity of embedded systems has become a problem due to their complexity and large-scale.
For the purpose of improving the productivity for embedded software development, the mruby on TECS framework has been proposed that is applied mruby (Lightweight Ruby) and supports component-based development.
In the current mruby on TECS, the mruby programs have to be compiled and linked every time the programs are modified because the mruby bytecodes are incorporated in the platform.
Moreover, while the framework supports multi-VM, developers needs to be familiar with the functions of real-time operating systems to effectively execute multiple mruby programs in concurrent or/and parallel.
In this paper, to improve the development efficiency, the mruby bytecode loader using Bluetooth is implemented as an extension of mruby on TECS.
In addition, multiple mruby programs run cooperatively in the proposed framework.
Experimental results demonstrates the advantages of the proposed framework.
\end{abstract}
\section{Introduction}
In these days, embedded systems have been required the high-quality and the high-performance.
Due to this trend, the complexity of embedded systems also increases and the scale is larger.
For example, IoT (Internet of Things) applications.
The low production cost and the short developing period of time are also needed.

@@

This paper proposes two additional features of mruby on TECS, mruby bytecode loader using Bluetooth and user-friendly multitask.
mruby on TECS has some problems at present.
One of these is that working efficiency is low because mruby on TECS only supports a SD card in the platform for LEGO MINDSTORMS EV3 to load mruby programs.
In the current development process, it is annoying that the SD card should be insert and pulled out repeatedly.
If a new feature, mruby bytecode loader Bluetooth, is used, the procedure is carried out only once at the beginning and a program code is transferred from a host to a target device by Bluetooth.
It can improve the efficiency.
Moreover, in the current system if developers attempt to run multiple tasks with the same priority, a task with first execution only runs and all other tasks would not run unless a OS's function must be called by developers.
In addition developers must prepare as many VMs as the number of threads because one RiteVM supports only one thread.
Thus that is a big burden on developers.
Another new feature enables developers to run a multitask programs more easily.
Specifically, a cycle handler of switching tasks is implemented.
This paper evaluates the proposed framework in term of data transfer rate, overhead of cyclic handler and execution time.

{\bf Contribution}: This paper proposes mruby bytecode loader using Bluetooth and user-friendly multitasking.
The proposed framework gives the contribution in the following points. 
\begin{enumerate}
\item To improve the  work efficiency in software development on mruby on TECS: \mbox{}\\
\ mruby bytecode loader using Bluetooth helps developers develop software.
Developers do not need to insert and pull out repeatedly and also to restart an OS.
Thus, the software development efficiency is improved.
\item To effectively execute multiple mruby programs in concurrent or/and parallel: \mbox{}\\
\ There is a probrem in multitasking of the current mruby on TECS.
It is that developers need to be well acquainted the RTOS if multiple mruby programs execute in multitasking. 
In the proposed framework, it is easy for developers to use multitasking because multiple tasks are switched cyclically.
Developers can easily program multitasking.
Multitasked programing makes the range of software expand.
\end{enumerate}

{\bf Organization}: The paper is organized as follows.
Section \ref{sec:Background} introduces the basic technologies i.e. mruby, TECS and mruby on TECS.
Section \ref{sec:mruby bytecode loader using Bluetooth} and Section \ref{sec:Multitask} describe the design and implementation of the proposed framework in detail.
Section \ref{sec:Evaluation} evaluates the proposed framework, Section \ref{sec:Related work} discuses related work, and then Section \ref{sec:Conclusion} concludes.

@@

\section{Evaluation}
\label{sec:Evaluation}
This section mentions experimental results and their consideration.
To analyze the advantages and disadvantages of the proposed framework, the evaluations are performed as follows.
\begin{itemize}
        \item the comparison of the size and transfer time between an mruby application including mruby libraries and not.
        \item the comparison of the overheads for each cyclic period of calling rot\_rdq.
        \item the comparison of the application execution time with singletasking, co-routine and multitasking.
\end{itemize}

@@

The 100,000 times loop program is used as mruby application for evaluation.
In detail, the singletask program loops 100,000 times, and the multitask and co-routine programs loop 50,000 times in each task.

The comparison of the application execution time with singletasking, co-routine and multitasking is shown in Figure \ref{fig:comparison_s_c_m}.
In Figure \ref{fig:comparison_s_c_m}, the cyclic time of the cyclic handler for multitasking is 1 msec.
Co-routine takes twice the time of singletask to execute an mruby application.
On the other hands, multitasking's execution time is about the same as singletasking's.

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/comparison_s_c_m.pdf}
    \caption{Comparison of the application execution time with singletask, co-routine and multitask}
    \label{fig:comparison_s_c_m}
\end{figure}

@@

\begin{table*}[t]
    \centering
    \caption{Comparion of the proposed and previous work}
    \begin{tabular}{c||c|ccc}
        & Bluetooth Loader & \shortstack{Preemptive-multitask\\(multi-VM)} & \shortstack{Nonpreemptive-multitask\\(co-routine)} & GIL \\ \hline
        mruby on TECS     &            & \checkmark & \checkmark &            \\
        mruby             &            &            & \checkmark &            \\
        Owl system        &            & -          & -          & \checkmark \\
        Lua               &            & -          & \checkmark &            \\
        Proposed framework& \checkmark & \checkmark & \checkmark &            \\
    \end{tabular}
    \label{tab:comparion}
\end{table*}
The open-source run-time systems for scripting languages have been developed such as follow: mruby on TECS \cite{7153813}, mruby \cite{5959588}, the Owl system \cite{180964}, and Lua \cite{Ierusalimschy:2007:EL:1238844.1238846}

@@

\section{Conclusion}
\label{sec:Conclusion}
This paper has presented the mruby bytecode loader using Bluetooth in multi-VM on mruby on TECS.
The proposed framework provides developers the efficient development without disconnecting a SD card and restarting an OS.
Furthermore, the proposed user-friendly multitasking can be used as the same as singletasking because of the low overhead.

%%%%%%%%%%%%%
% Reference %
%%%%%%%%%%%%%
\bibliography{ref.bib}
